Research log

### 2024-01-09 docs/ExploratoryResults.Rmd
online materials

This last finding bears emphasizing: In both classes two and three, pretenders *knew* that they had just sunk a size-two ship, but in the second case they *pretended not to know* this fact, and this affected their their response latency in the same way it would have been affected had they been in a non-pretend game.

@@

```{r half-games, echo=FALSE, out.width = '100%', fig.cap = "Half games. First column: the two boards, as they appeared to pretenders. Second column: objective hit probability, given game state. Third and fourth columns: empirical click probabilities in non-pretend and pretend games, respectively."}
knitr::include_graphics("figures/Half_games.png")
```
## Heuristic use

@@

Flexibility scores increased as a function of click number for both pretend and non-pretend games, as expected if players adjust their behaviour based on the outcomes of previous clicks. This process reached a plateau of around $H=2.1$ at click number 6.

@@

In the following analysis, we focus on the first two labels and carve out two sets of players: `r E2.suppressors%>%length` players who reported using suppression but not simulation, and `r E2.simulators%>%length` who reported using simulation but not suppression.

@@

The mean negative optimality score of non-pretend games was `r E2.sup_sim.mean_P_click_rank%>%filter(group=='suppressors' & test_part=='nonpretend') %>%pull(p_click_rank)%>%mean()` among suppressors and `r E2.sup_sim.mean_P_click_rank%>%filter(group=='simulators' & test_part=='nonpretend') %>%pull(p_click_rank)%>%mean()` among simulators (`r apa_print(t.test(E2.sup_sim.mean_P_click_rank%>%filter(group=='suppressors' & test_part=='nonpretend') %>%pull(p_click_rank), E2.sup_sim.mean_P_click_rank%>%filter(group=='simulators' & test_part=='nonpretend') %>%pull(p_click_rank)))$statistic`). The mean negative optimality score of pretend games was `r E2.sup_sim.mean_P_click_rank%>%filter(group=='suppressors' & test_part=='pretend') %>%pull(p_click_rank)%>%mean()` among suppressors and `r E2.sup_sim.mean_P_click_rank%>%filter(group=='simulators' & test_part=='pretend') %>%pull(p_click_rank)%>%mean()` among simulators (`r apa_print(t.test(E2.sup_sim.mean_P_click_rank%>%filter(group=='suppressors' & test_part=='pretend') %>%pull(p_click_rank), E2.sup_sim.mean_P_click_rank%>%filter(group=='simulators' & test_part=='pretend') %>%pull(p_click_rank)))$statistic`). To the very least, simulators did as well as suppressors in pretending.

@@

Like for Battleship, flexibility scores increased as a function of click number for both pretend and non-pretend games, as expected if players adjust their behaviour based on the outcomes of previous clicks. This process reached a plateau of around $H=2$ and click number 6.

@@

To quantify the contribution of each of these factors to letter selection, we fitted a multinomial logistic regression model to the data of each player. We compared the ensuing coefficients in 'pretend' and 'non-pretend' conditions.

@@

Given colinearity between model predictors, we suspected that the effects of expected information gain may be driven by posterior probability effects.  To isolate unique contributions of prior probability and expected information gain, we repeated the same analysis, but this time serially orthogonalizing the features (in the order [posterior, prior, expected information gain], and using the Gram Schmidt algorithm) prior to fitting the multinomial regression model. This time, expected information gain had no significant effect on decision in non-pretend (`r  apa_print(E4.model_coefficients_orth%>%filter(test_part=='nonpretend')%>%pull(eig)%>%t.test())$statistic`) and pretend games (`r  apa_print(E4.model_coefficients_orth%>%filter(test_part=='pretend')%>%pull(eig)%>%t.test())$statistic`), rendering it possible that the previously observed effects were confounded with prior and posterior probability. In contrast, both prior and posterior probability had a significant positive effect, with prior probability having a stronger effect in pretend games (`r apa_print(E4.model_coefficients_orth %>% dplyr::select(subj_id,test_part,prior)%>%spread(test_part,prior)%>%mutate(diff=pretend-nonpretend)%>%pull(diff)%>%t.test())$full_result`).

@@

At the end of the experiment, players were asked whether they had a strategy for pretending or for detecting pretense. I (MM) manually labeled their responses according to three criteria: mentions of suppression (e.g., "Trying to ignore the hints"), simulation (e.g., "Trying to imagine how I would react"), and rules (e.g., "Checking the corners and center before random selection of tiles"). Some answers got more than one label and some got none. Overall, `r E4.debrief_labeled$suppression%>%sum()` mentioned using suppression, `r E4.debrief_labeled$simulation%>%sum()` mentioned using simulation, and `r E4.debrief_labeled$heuristic%>%sum()` mentioned following a heuristic.

>>>>

This last finding bears emphasizing: In both classes two and three, pretenders *knew* that they had just sunk a size-two ship, but in the second case they *pretended not to know* this fact, and this affected their response latency in the same way it would have been affected had they been in a non-pretend game.

@@

```{r half-games, echo=FALSE, out.width = '100%', fig.cap = "Half games. First column: the two boards, as they appeared to pretenders. Second column: objective hit probability, given game state. Third and fourth columns: empirical click probabilities in non-pretend and pretend games, respectively."}
knitr::include_graphics("figures/Half_games.png")
```

## Heuristic use

@@

Flexibility scores increased as a function of click number for both pretend and non-pretend games, as expected if players adjust their behavior based on the outcomes of previous clicks. This process reached a plateau of around $H=2.1$ at click number 6.

@@

In the following analysis, we focus on the first two labels and sort players into two groups: `r E2.suppressors%>%length` players who reported using suppression but not simulation, and `r E2.simulators%>%length` who reported using simulation but not suppression.

@@

The mean negative optimality score of non-pretend games was `r E2.sup_sim.mean_P_click_rank%>%filter(group=='suppressors' & test_part=='nonpretend') %>%pull(p_click_rank)%>%mean()%>%printnum()` among suppressors and `r E2.sup_sim.mean_P_click_rank%>%filter(group=='simulators' & test_part=='nonpretend') %>%pull(p_click_rank)%>%mean()%>%printnum()` among simulators (`r apa_print(t.test(E2.sup_sim.mean_P_click_rank%>%filter(group=='suppressors' & test_part=='nonpretend') %>%pull(p_click_rank), E2.sup_sim.mean_P_click_rank%>%filter(group=='simulators' & test_part=='nonpretend') %>%pull(p_click_rank)))$statistic`). The mean negative optimality score of pretend games was `r E2.sup_sim.mean_P_click_rank%>%filter(group=='suppressors' & test_part=='pretend') %>%pull(p_click_rank)%>%mean()%>%printnum()` among suppressors and `r E2.sup_sim.mean_P_click_rank%>%filter(group=='simulators' & test_part=='pretend') %>%pull(p_click_rank)%>%mean()%>%printnum()` among simulators (`r apa_print(t.test(E2.sup_sim.mean_P_click_rank%>%filter(group=='suppressors' & test_part=='pretend') %>%pull(p_click_rank), E2.sup_sim.mean_P_click_rank%>%filter(group=='simulators' & test_part=='pretend') %>%pull(p_click_rank)))$statistic`). Note that a higher score here means lower optimality. To the very least, simulators did as well as suppressors in pretending.

@@

Like for Battleship, flexibility scores increased as a function of click number for both pretend and non-pretend games, as expected if players adjust their behavior based on the outcomes of previous clicks. This process reached a plateau of around $H=2$ and click number 6.

@@

To quantify the contribution of each of these factors to letter selection, we fitted a multinomial logistic regression model to the data of each player. The model was specified and fit using the Turing Julia library for Bayesian inference with probabilistic programming [@ge2018]. We compared the ensuing coefficients in 'pretend' and 'non-pretend' conditions.

@@

Given collinearity between model predictors, we suspected that the effects of expected information gain may be driven by posterior probability effects. To isolate unique contributions of prior probability and expected information gain, we repeated the same analysis, but this time serially orthogonalizing the features (in the order [posterior, prior, expected information gain], and using the Gram Schmidt algorithm) prior to fitting the multinomial regression model. This time, expected information gain had no significant effect on decisions in non-pretend (`r  apa_print(E4.model_coefficients_orth%>%filter(test_part=='nonpretend')%>%pull(eig)%>%t.test())$statistic`) and pretend games (`r  apa_print(E4.model_coefficients_orth%>%filter(test_part=='pretend')%>%pull(eig)%>%t.test())$statistic`), rendering it possible that the previously observed effects were confounded with prior and posterior probability. In contrast, both prior and posterior probability had a significant positive effect, with prior probability having a stronger effect in pretend games (`r apa_print(E4.model_coefficients_orth %>% dplyr::select(subj_id,test_part,prior)%>%spread(test_part,prior)%>%mutate(diff=pretend-nonpretend)%>%pull(diff)%>%t.test())$full_result`).

@@

At the end of the experiment, players were asked whether they had a strategy for pretending or for detecting pretense. I (MM) manually labeled their responses according to three criteria: mentions of suppression (e.g., "I just tried to forget what the word was"), simulation (e.g., " I tried to focus on how I would have deduced the word if I hadn't known it"), and rules (e.g., "I started with vowels in the order we receive them in school"). Some answers got more than one label and some got none. Overall, `r E4.debrief_labeled$suppression%>%sum()` mentioned using suppression, `r E4.debrief_labeled$simulation%>%sum()` mentioned using simulation, and `r E4.debrief_labeled$heuristic%>%sum()` mentioned following a heuristic.

### 2024-01-09 docs/preregisteredMethodsAndResults.Rmd
online materials

E2.performance_df %>%
  ggplot(aes(x=pretend_rate, y=judge_rate)) +
  geom_point() +
  labs(x= 'successful pretense rate', y='judge accuracy') +
  theme_classic()

@@

The research complied with all relevant ethical regulations and was approved by the Research Ethics Committee of Johns Hopkins University. 500 Participants were recruited via Prolific (prolific.co) and gave their informed consent prior to their participation. They were selected based on their acceptance rate (\>95%) and for being native English speakers. The entire experiment took approximately 20 minutes to complete. Participants' pay was equivalent to an hourly wage of 9.50 USD, in addition to a bonus payment of 1 USD that was awarded to `r E4.bonus$bonus%>%sum(na.rm=T)` players who earned 100 points or more.

@@

The median game duration in non-pretend games was `r round(E4.median_time$nonpretend%>%median())` seconds in non-pretend games and `r round(E4.median_time$nonpretend%>%median())` seconds in pretend games. Pretend games were significantly shorter among subjects that pretended in the first block (`r apa_print(E4.median_time%>%filter(!genuine_first)%>%pull(diff)%>%t.test())$statistic`) and in the second block (`r apa_print(E4.median_time%>%filter(genuine_first)%>%pull(diff)%>%t.test())$statistic`).

@@

Letter selections preceding a hit were faster than those preceding a miss in non-pretend games only in the group that pretended first (`r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & !genuine_first)%>%pull(nonpretend)%>%t.test())$full_result`) but not in the group that played normally first (`r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & genuine_first)%>%pull(nonpretend)%>%t.test())$full_result`). This effect was not observed in pretend games (pretend first: `r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & !genuine_first)%>%pull(pretend)%>%t.test())$full_result`; non-pretend first: `r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & genuine_first)%>%pull(pretend)%>%t.test())$full_result`). We find a significant interaction between these effects in the group that pretended first (`r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & !genuine_first)%>%pull(interaction)%>%t.test())$full_result`) but not in the other group (`r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & genuine_first)%>%pull(interaction)%>%t.test())$full_result`). The difference was not significant when analyzing first blocks only (`r apa_print(t.test(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & genuine_first)%>%pull(nonpretend),E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & !genuine_first)%>%pull(pretend)))$statistic`).

@@

The next analyses were designed to test for differences in game optimality between pretend and non-pretend games, and for a relationship between decision difficulty and click latency. To do so, we approximated optimal behaviour by approximating the posterior probability that a letter appears in the word, given available information. Critically, in modelling pretend games we do not treat hints as part of this available information, because an optimal player should ignore this information in choosing where to click next. Given this posterior, a rational player should choose letters that have a high posterior probability of appearing in the word.

@@

Letter selections in pretend games had a higher posterior probability to be included in the word than in random games (pretend first: `r E4.mean_P_click_rank_wide%>%filter(!genuine_first)%>%pull(np_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_P_click_rank_wide%>%filter(genuine_first)%>%pull(np_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`). The same was true for letter selections in pretend games (pretend first: `r E4.mean_P_click_rank_wide%>%filter(!genuine_first)%>%pull(p_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_P_click_rank_wide%>%filter(genuine_first)%>%pull(p_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`). Non-pretend letter selections had a higher posterior probability among players who pretended first (`r E4.mean_P_click_rank_wide%>%filter(!genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`) but not in the group that played normally first (`r E4.mean_P_click_rank_wide%>%filter(genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`). Comparing data from the first condition only in a between-subject manner revealed a significant difference (`r t.test(E4.mean_P_click_rank_wide%>%filter(genuine_first)%>%pull(nonpretend),E4.mean_P_click_rank_wide%>%filter(!genuine_first)%>%pull(pretend))%>%apa_print%>%'$'(full_result)`).

@@

Non-pretenders selected high-frequency letters more than expected by chance (pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(!genuine_first)%>%pull(np_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(genuine_first)%>%pull(np_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`). The same was true for letter selections in pretend games (pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(!genuine_first)%>%pull(p_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(genuine_first)%>%pull(p_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`). Letters selected by pretenders had a higher overall frequency compared to letters selected by non-pretenders (pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(!genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`). but not in the group that played normally first (`r E4.mean_letter_prob_P_click_rank_wide%>%filter(genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`). Comparing data from the first condition only in a between-subject manner revealed a significant difference (`r t.test(E4.mean_P_click_rank_wide%>%filter(genuine_first)%>%pull(nonpretend),E4.mean_P_click_rank_wide%>%filter(!genuine_first)%>%pull(pretend))%>%apa_print%>%'$'(full_result)`).

This was the case also when focusing on misses only ( pretend first: `r E4.mean_letter_prob_P_click_rank_misses_wide%>%filter(!genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_P_click_rank_misses_wide%>%filter(genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`; first block only: `r t.test(E4.mean_P_click_rank_misses_wide%>%filter(genuine_first)%>%pull(nonpretend),E4.mean_P_click_rank_misses_wide%>%filter(!genuine_first)%>%pull(pretend))%>%apa_print%>%'$'(full_result)`).

@@

Participants were not significantly above chance in judging whether the presented game came from a pretender (`r apa_print(t.test(E4.judge_summary_df$accuracy, mu=0.5))$full_result`). This was the case also when focusing on words that judges encountered when pretending (`r apa_print(t.test(E4.judge_summary_df$accuracy_pretend_words, mu=0.5))$full_result`), and when focusing on words that judges encountered when playing normally (`r apa_print(t.test(E4.judge_summary_df$accuracy_nonpretend_words, mu=0.5))$full_result`).

@@

p <- E4.performance_df %>%
  ggplot(aes(x=judge_rate,y=pretend_rate)) +
  geom_jitter() + 
  labs(x='judge accuracy',y='pretense success rate') +
  theme_classic()

@@

E4.performance_df %>%
  ggplot(aes(x=pretend_rate, y=judge_rate)) +
  geom_point() +
  labs(x= 'successful pretense rate', y='judge accuracy') +
  theme_classic()

@@

### Hypothesis 12 (irrational letter selections)

In non-pretend games, subjects almost always chose letters that made sense (pretend-first group: `r E4.first_click_half_games %>% filter(test_part=='nonpretend_half_game' & genuine_first=='False')%>%pull(makes_sense)%>%mean()%>%printnum()`; pretend-second group: `r E4.first_click_half_games %>% filter(test_part=='nonpretend_half_game' & genuine_first=='True')%>%pull(makes_sense)%>%mean()%>%printnum()`). In pretend games, these figures were significantly lower (pretend-first group: `r E4.first_click_half_games %>% filter(test_part=='pretend_half_game' & genuine_first=='False')%>%pull(makes_sense)%>%mean()%>%printnum()`, $p<.001$; pretend-second group: `r E4.first_click_half_games %>% filter(test_part=='pretend_half_game' & genuine_first=='True')%>%pull(makes_sense)%>%mean()%>%printnum()`, $p<.001$).

@@

### Hypothesis 13 (target word effect)

>>>>

E2.performance_df %>%
  group_by(judge_rate,pretend_rate)%>%
  summarise(n=n())%>%
  ggplot(aes(x=judge_rate,y=pretend_rate,size=n)) +
  geom_point()+
  labs(x='judge accuracy',y='pretense success rate') +
  theme_classic()+
  theme(legend.pos='na')

ggsave('figures/Battleship2/judge_pretend_accuracy.png',dpi=300)

@@

The research complied with all relevant ethical regulations and was approved by the Research Ethics Committee of Johns Hopkins University. 501 Participants were recruited via Prolific (prolific.co) and gave their informed consent prior to their participation. They were selected based on their acceptance rate (\>95%) and for being native English speakers. The entire experiment took approximately 20 minutes to complete. Participants' pay was equivalent to an hourly wage of 9.50 USD, in addition to a bonus payment of 1 USD that was awarded to `r E4.bonus$bonus%>%sum(na.rm=T)` players who earned 100 points or more.

@@

The median game duration in non-pretend games was `r round(E4.median_time$nonpretend%>%median())` seconds in non-pretend games and `r round(E4.median_time$pretend%>%median())` seconds in pretend games. Pretend games were significantly shorter among subjects that pretended in the first block (`r apa_print(E4.median_time%>%filter(!genuine_first)%>%pull(diff)%>%t.test())$statistic`) and in the second block (`r apa_print(E4.median_time%>%filter(genuine_first)%>%pull(diff)%>%t.test())$statistic`).

@@

Letter selections preceding a hit were faster than those preceding a miss in non-pretend games only in the group that pretended first (`r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & !genuine_first)%>%pull(nonpretend)%>%t.test())$statistic`) but not in the group that played normally first (`r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & genuine_first)%>%pull(nonpretend)%>%t.test())$statistic`). This effect was not observed in pretend games (pretend first: `r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & !genuine_first)%>%pull(pretend)%>%t.test())$statistic`; non-pretend first: `r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & genuine_first)%>%pull(pretend)%>%t.test())$statistic`). We find a significant interaction between these effects in the group that pretended first (`r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & !genuine_first)%>%pull(interaction)%>%t.test())$statistic`) but not in the other group (`r apa_print(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & genuine_first)%>%pull(interaction)%>%t.test())$statistic`). The difference was not significant when analyzing first blocks only (`r apa_print(t.test(E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & genuine_first)%>%pull(nonpretend),E4.RT_by_hit_lags_by_condition%>%filter(position==-1 & !genuine_first)%>%pull(pretend)))$statistic`).

@@

The next analyses were designed to test for differences in game optimality between pretend and non-pretend games, and for a relationship between decision difficulty and click latency. To do so, we approximated optimal behavior by approximating the posterior probability that a letter appears in the word, given available information. Critically, in modelling pretend games we do not treat hints as part of this available information, because an optimal player should ignore this information in choosing where to click next. Given this posterior, a rational player should choose letters that have a high posterior probability of appearing in the word.

@@

Letter selections in non-pretend games had a higher posterior probability to be included in the word than in random games (pretend first: `r E4.mean_P_click_rank_wide%>%filter(!genuine_first)%>%pull(np_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_P_click_rank_wide%>%filter(genuine_first)%>%pull(np_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`). The same was true for letter selections in pretend games (pretend first: `r E4.mean_P_click_rank_wide%>%filter(!genuine_first)%>%pull(p_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_P_click_rank_wide%>%filter(genuine_first)%>%pull(p_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`). Non-pretend letter selections had a higher posterior probability than pretend letter selections among players who pretended first (`r E4.mean_P_click_rank_wide%>%filter(!genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`) but not in the group that played normally first (`r E4.mean_P_click_rank_wide%>%filter(genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`). Comparing data from the first condition only in a between-subject manner revealed a significant difference (`r t.test(E4.mean_P_click_rank_wide%>%filter(genuine_first)%>%pull(nonpretend),E4.mean_P_click_rank_wide%>%filter(!genuine_first)%>%pull(pretend))%>%apa_print%>%'$'(full_result)`).

@@

Non-pretenders selected high-frequency letters more than expected by chance (pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(!genuine_first)%>%pull(np_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(genuine_first)%>%pull(np_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`). The same was true for letter selections in pretend games (pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(!genuine_first)%>%pull(p_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(genuine_first)%>%pull(p_vs_r)%>%t.test()%>%apa_print%>%'$'(statistic)`). Letters selected by pretenders had a higher overall frequency compared to letters selected by non-pretenders (pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(!genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_letter_prob_P_click_rank_wide%>%filter(genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`). Comparing data from the first condition only in a between-subject manner revealed a significant difference (`r t.test(E4.mean_P_click_rank_wide%>%filter(genuine_first)%>%pull(nonpretend),E4.mean_P_click_rank_wide%>%filter(!genuine_first)%>%pull(pretend))%>%apa_print%>%'$'(full_result)`).

When focusing on misses only, pretend letter selections were again more aligned with the frequency of letters in English words than were non-pretend letter selections ( pretend first: `r E4.mean_letter_prob_P_click_rank_misses_wide%>%filter(!genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`; non-pretend first: `r E4.mean_P_click_rank_misses_wide%>%filter(genuine_first)%>%pull(p_vs_np)%>%t.test()%>%apa_print%>%'$'(statistic)`; first block only: `r t.test(E4.mean_P_click_rank_misses_wide%>%filter(genuine_first)%>%pull(nonpretend),E4.mean_P_click_rank_misses_wide%>%filter(!genuine_first)%>%pull(pretend))%>%apa_print%>%'$'(full_result)`).

@@

Participants were not significantly above chance in judging whether the presented game came from a pretender or from a genuine player (`r apa_print(t.test(E4.judge_summary_df$accuracy, mu=0.5))$full_result`). This was the case also when focusing on words that judges encountered when pretending (`r apa_print(t.test(E4.judge_summary_df$accuracy_pretend_words, mu=0.5))$full_result`), and when focusing on words that judges encountered when playing normally (`r apa_print(t.test(E4.judge_summary_df$accuracy_nonpretend_words, mu=0.5))$full_result`).

@@

p <- E4.performance_df %>%
  group_by(judge_rate,pretend_rate)%>%
  summarise(n=n())%>%
  ggplot(aes(x=judge_rate,y=pretend_rate,size=n)) +
  labs(x='judge accuracy',y='pretense success rate') +
  theme_classic()+
  theme(legend.pos='na')

@@

E4.performance_df %>%
  group_by(pretend_rate,judge_rate) %>%
  summarise(n=n()) %>% 
  ggplot (aes(x=pretend_rate,y=judge_rate,size=n)) +
  geom_point() +
  labs(x= 'successful pretense rate', y='judge accuracy') +
  theme_classic()+
  theme(legend.pos='na')

ggsave('figures/Hangman2/judge_pretend_accuracy.png',p,dpi=300)
```

@@

### Hypothesis 12 (irrational letter selections in half-games)

In non-pretend games, subjects almost always chose letters that made sense, that is, that were consistent with at least one word that matched the presented category and game state (pretend-first group: `r E4.first_click_half_games %>% filter(test_part=='nonpretend_half_game' & genuine_first=='False')%>%pull(makes_sense)%>%mean()%>%printnum()`; pretend-second group: `r E4.first_click_half_games %>% filter(test_part=='nonpretend_half_game' & genuine_first=='True')%>%pull(makes_sense)%>%mean()%>%printnum()`). In pretend games, these figures were significantly lower (pretend-first group: `r E4.first_click_half_games %>% filter(test_part=='pretend_half_game' & genuine_first=='False')%>%pull(makes_sense)%>%mean()%>%printnum()`, $p<.001$; pretend-second group: `r E4.first_click_half_games %>% filter(test_part=='pretend_half_game' & genuine_first=='True')%>%pull(makes_sense)%>%mean()%>%printnum()`, $p<.001$).

@@

### Hypothesis 13 (target word effect in half-games)
